---
title: "introduction"
author: "Dimitris Kavroudakis"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    keep_md: true
    fig_caption: yes
    fig_width: 5
    fig_height: 5
  rmarkdown::pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## Introduction

Use of goal package
'uav' group of functions
goaldata.data2

  

## Example Data in _goal_ package

The goal package includes a sample dataset for the presentation of the _uav_ examples. 

```{r, fig.show='hold'}
library(goal)
data("goaldata.data2", package = "goal")
plot(goaldata.data2) 

#xy=data.frame(x=c(25.92548,25.92970,25.92927,25.92489,25.92548), y=c(39.13743,39.13591,39.13500,39.13641,39.13743 )) 
library(sp)
#coordinates(xy) <- ~x+y
#plot(xy)
```

These `r nrow(goaldata.data2)` points define a polygon area which is the area of our case study.
We then use the _'uav.GenerateTargets'_ function to generate all possible targets in this area.

 


```{r , warning=F, fig.cap = "Your figure caption."}
one = uav.GenerateTargets(goaldata.data2)

par(mar=c(0, 0, 0, 0))
plot(one$Polygon)
plot(one$simia, col= as.numeric(as.factor(one$simia$type)), add=TRUE,  
     pch=3*as.numeric(as.factor(one$simia$type)) )
plot(one$lines, add=T)
text(one$simia , labels = one$simia$id, col="brown", pos=2)
#library(rgdal)
#rgdal::writeOGR(one$simia,dsn=paste0("Targets.shp"),layer="Targets",driver="ESRI Shapefile", overwrite_layer = T)

```

As you can see in the figure above, we generated `r nrow(one$simia)` targets inside this polygon. These points are quite a few, and we do need to reduce them. We use the _'uav.DoReduction'_ function for reducing them based on the density of points. 

When using the _'uav.DoReduction'_ function we need to define a cell size which will be used for the calculation of points density.

The plots bellow, show the calculation of focal density of points, under various cell sizes (5, 10, 15), in the study area and return a frequency table of number of cells per pixels:

```{r , warning=F, fig.cap =c("one","two","three"), results='asis', fig.height=5}
library(knitr)

par(mar=c(0, 0, 3, 0))
five = uav.showFocal(insimia = one$simia, inpol=one$Polygon, toplot = T, size = 5) 
kable(as.data.frame(five), col.names=c("Number of points","Frequency"))

ten = uav.showFocal(insimia = one$simia, inpol=one$Polygon, toplot = T, size = 10)
kable(as.data.frame(ten), col.names=c("Number of points","Frequency"))

fifteen = uav.showFocal(insimia = one$simia, inpol=one$Polygon, toplot = T, size = 15)
 kable(as.data.frame(fifteen), col.names=c("Number of points","Frequency"))
```
 
Points Reduction
===

Now we will use focal size 10 and will reduce the points in the area. We use the '_DoReduction_' function:
```{r , warning=F, fig.cap =c("one","two","three"), results='asis', fig.height=5}
result = goal::uav.DoReduction(one, insize=10)

par(mar=c(0, 0, 3, 0))
plot(one$Polygon, main=paste0(length(one$simia)," initial points in grey\n",length(result)," final points in blue"))
#plot(one$simia, col="blue", add=TRUE, pch=20)
plot(one$simia,  add=TRUE, col="grey")
text(one$simia, labels=one$simia$id, pos=4, col="grey")

plot(result, col="blue", pch=20, add=TRUE)
text(result, labels=result$id, pos=2, col="navyblue")
```

