---
title: "OpenStreetMap"
author: "Dimitris Kavroudakis"
date: "`r Sys.Date()`"
description: "POIs density in a city. Network analysis of roads in a city."
output: 
  rmarkdown::html_vignette:
    toc: true
    keep_md: true
    fig_caption: yes
    fig_width: 5
    fig_height: 5
  rmarkdown::pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{OpenStreetMap}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Introduction

Use of `goal` package and more specificaly the 'osm' group of functions for the analysis of [OpenStreetMap](https://www.openstreetmap.org) POIs (Points of Interest) and road network. The following two links, can help on identifying OSM entities (Municipalities, cities, ...)

* [Search OSM](https://nominatim.openstreetmap.org/ui/search.html)

* [Bounding BOX](http://bboxfinder.com/#39.073311,26.516018,39.123935,26.584167)

  

## POIs analysis

Aim: Analyse the location of Amenities and Shops in this municipality.
First install `goal` library
```{r}
library(devtools)
devtools::install_github("dimitrisk/goal", quiet=T)
library(goal)
#library(osmdata)
library(raster)
```

### Amenities

Download all amenities in this municipality (Points or Polygons or Multipolygons)
```{r}
am = osm.getPOI(inPerioxi = "Mytilene Municipal Unit", inkey = "amenity")
am
```

Alternatively, we can use a bounding box of an area instead of the name of a municipality.
```{r}
myt = osm.getPOI_usingbb( c(26.547303,39.101658,26.564641,39.113247), inkey ="amenity" )
myt
```

After downloading the POIs (`am`), we merge all POIs together (Points, Polygons, Multipolygons), 
and convert them all to points.
```{r}
amenities = osm.combineAmenities(am)
amenities
```

Frequency table of amenities types in this municipality
```{r}
freq1 = osm.getFrequency(amenities, inword = "amenity", removeNA = F)
freq1
```



 
### Shops


Get all shops in this municipality (Points, Polygons, Multipolygons)
```{r}
sh = osm.getPOI(inPerioxi = "Mytilene Municipal Unit", inkey = "shop")
sh

#' Merge all shops (Points, Polygons, Multipolygons), and convert them to points.
shops = osm.combineShops(sh)
shops
```

Frequency table of shop types in this municipality
```{r}
freq2 = osm.getFrequency(shops, inword = "shop", removeNA = F)
freq2
```


### Density
 
Create empty raster of this area and get the polygon of this area.
```{r}
r = osm.CreateEmptyRaster(inPerioxi = "Mytilene Municipal Unit")

#' Get polygon of the area
mypol = osmdata::getbb("Mytilene Municipal Unit", format_out = "sf_polygon")$multipolygon
```

Sum of shops per cell
```{r}
density1 = raster::rasterize(shops, r, field=1, fun=sum) # sum
plot(density1)
plot(mypol, add=T)
```

Sum of amenities per cell
```{r}
density2 = raster::rasterize(amenities, r, field=1, fun=sum) # sum
plot(density2)
plot(mypol, add=T)
```



### Presense/Absense

Presense/Absence of shops in cells
```{r }
presense1 = raster::rasterize(shops, r, field=1) # presense
plot(presense1)
plot(mypol, add=T)
```

Presense/Absence of shops in cells
```{r }
presense2 = raster::rasterize(amenities, r, field=1) # presense
plot(presense2)
plot(mypol, add=T)
```

### Web Map

```{r message=F, warn=F}
#' web map1
library(leaflet)
leaflet(amenities) %>% addTiles() %>%  leaflet::addMarkers(popup = ~as.character(amenity), label = ~as.character(amenity))

#' web map2
library(simplevis)
library(dplyr)
library(palmerpenguins)
library(stars)
leaf_sf_col(amenities,  col_var = amenity)
```


### Custom bounding box

We now use a custom bounding box and then download data only for this area.
```{r}
am = osm.getPOI_usingbb( c(26.547303,39.101658,26.564641,39.113247), inkey ="amenity" ) # Download
mypol_bb = osm.osmdata_result_2_bbox_pol(am) # get polygon of this bounding box.
amenities = osm.combineAmenities(am) # combine all amenities into points.
```

Now get the general polygon of this municipality (coastline)
```{r}
mypol2 = osmdata::getbb("Mytilene Municipal Unit", format_out = "sf_polygon")$multipolygon
```


```{r}
q=c(26.545029,39.088569,26.570177,39.116810)
poly = bb_2_pol(q, outcrs=2100) 
plot(poly)
```

What we have so far:
```{r}
plot(mypol2, border="red")
plot(mypol_bb, add=T)
plot(amenities, add=T)
```

zoomed in:
```{r}
plot(mypol_bb )
plot(mypol2, border="red", add=T)
plot(amenities, add=T)
```


We need to calculate the intersection between municipality polygon (coastline) and the 
custom square bounding box we have defined.

```{r}
clip1 = sf::st_intersection(mypol_bb,mypol2)
```

show the area
```{r}
plot(clip1)
plot(mypol2, border="red", add=T)
plot(amenities, add=T)
```

Create an empty raster of this intersection:
```{r}
r = raster(clip1 )
```

Calculate the density of amenities (points) in this clipped area:
```{r}
density1 = raster::rasterize(amenities, r, field=1, fun=sum) # sum
plot(density1)
plot(clip1, add=T)
plot(as_Spatial(amenities), add=T, cex=0.5)
```


## Road network analysis

Get all roads of this municipality by using just the municipality name:
```{r}
myr1 = osm.getRoads(inPerioxi = "Mytilene Municipal Unit", 
                    withBB=FALSE, outcrs = 2100)
myr1
plot(myr1)
```

Get all roads of this area by using a bounding box:
```{r}
myr2 = osm.getRoads(incoordinates = c(26.545029,39.088569,26.570177,39.116810), 
                    withBB=TRUE, outcrs = 2100 )
myr2
plot(myr2)
```
